---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BayesianLaterality

<!-- badges: start -->
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/BayesianLaterality)](https://cran.r-project.org/package=BayesianLaterality)
<!-- badges: end -->

BayesianLaterality contains a function for predicting latent hemispheric dominance based on observed laterality using a Bayes classifier developed by [Sørensen and Westerhausen (2020)](https://doi.org/10.1080/1357650X.2020.1769124). See also the [accompanying Shiny app](https://osorensen.shinyapps.io/BayesianLateralityApp/).

## Installation


You can install BayesianLaterality from [CRAN](https://cran.r-project.org/web/packages/BayesianLaterality/) with:

```{r, eval=FALSE}
install.packages("BayesianLaterality")
```

Install the latest development version from [GitHub](https://github.com/LCBC-UiO/BayesianLaterality) with:

``` r
# install.packages("remotes")
remotes::install_github("LCBC-UiO/BayesianLaterality")
```


## Application Example

```{r}
library(BayesianLaterality)
```


The main (and only) function of the package is `predict_dominance()`. To see the arguments that can be set by the user and a more extended example, type `?predict_dominance` in the R terminal. Here is a simple example. The dataset `example_data1` contains three laterality measurements on three right-handed individuals.

```{r}
example_data1
```

We then obtain predicted hemispheric dominance as follows. The ID column reflects the row in the original dataset.

```{r}
predict_dominance(example_data1)
```


