---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BayesianLaterality

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/LCBC-UiO/BayesianLaterality.svg?branch=master)](https://travis-ci.org/LCBC-UiO/BayesianLaterality)
<!-- badges: end -->

BayesianLaterality contains a function for predicting latent hemispheric dominance based on observed laterality using a Bayes classifier developed by [Sørensen and Westerhausen (2020)](https://doi.org/10.31234/osf.io/yvmxc).

## Installation


You can install BayesianLaterality from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("LCBC-UiO/BayesianLaterality")
```


## Application Example

```{r}
library(BayesianLaterality)
```


The main (and only) function of the package is `predict_dominance()`. To see the arguments that can be set by the user and a more extended example, type `?predict_dominance` in the R terminal. Here is a simple example. The dataset `example_data1` contains three laterality measurements on three right-handed individuals.

```{r}
example_data1
```

We then obtain predicted hemispheric dominance as follows. The ID column reflects the row in the original dataset.

```{r}
predict_dominance(example_data1)
```


